Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-10 paper_io_sim.tex

    In this work, we present WRENCH-cache, a simulation model of I/O
    with page cache incorporated into the WRENCH simulation framework~\cite{casanova2020fgcs},
    which is  based on the popular SimGrid distributed simulation framework~\cite{casanova2014simgrid}.
    The added value of WRENCH-cache is to make it possible to simulate 
        application execution accurately in the presence of page caching. Our specific 
        contributions are as follows:
    \begin{compactitem}
        \item A page cache simulation model that supports 
    both single-threaded and multithreaded applications, and of both
    writeback and writethrough caches for local or network-based
    filesystems;
        \item An implementation of this model in WRENCH; 
        \item An evaluation and validation of the accuracy of our model, and of its implementation,
              for a range of applications, platforms, and page cache configurations. 
    \end{compactitem}

>>>>

    In this work, we present WRENCH-cache, a simulation model of I/O
    with page cache incorporated into the WRENCH simulation framework~\cite{casanova2020fgcs},
    which is  based on the popular SimGrid distributed simulation framework~\cite{casanova2014simgrid}.
    The added value of WRENCH-cache is to make it possible to simulate 
        application execution accurately in the presence of page caching. Our specific 
        contributions are as follows:
    \begin{compactitem}
        \item A page cache simulation model that supports 
    both single-threaded and multithreaded applications, and of both
    writeback and writethrough caches for local or network-based
    filesystems;
        \item An implementation of this model in WRENCH; 
        \item An evaluation of the accuracy and scalability of our model, and of its implementation,
              for a range of applications, platforms, and page cache configurations. 
    \end{compactitem}
